
\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\geometry{margin=2cm}
\pagestyle{empty}
\setlist[itemize]{noitemsep, topsep=0pt}

\definecolor{main}{RGB}{33, 37, 41}
\definecolor{accent}{RGB}{108, 117, 125}

\newcommand{\sectiontitle}[1]{\vspace{1.2em}\textbf{\Large #1}\vspace{0.5em}\\}
\newcommand{\job}[3]{\textbf{#1} -- #2\\\textit{#3}\\}
\newcommand{\skill}[1]{\textbf{#1}}

\begin{document}
\begin{center}
    {\Huge \textbf{Clément Désiles}}\\
    \vspace{0.2cm}
    \href{mailto:jobs@clementdesiles.fr}{jobs@clementdesiles.fr} \textbullet{} +33 6 58 12 45 61 \textbullet{} \href{https://clementdesiles.fr}{clementdesiles.fr}
\end{center}

\sectiontitle{Objective}
Engineer passionate about \textbf{software craftsmanship} and \textbf{technical leadership}, looking for a position as \textbf{Engineering Manager} to help teams reach both technical and human excellence.

\sectiontitle{Professional Experience}

\job{Engineering Manager – PrestaShop (Remote)}{Aug 2022 – Feb 2025}{2 yrs 8 mos}
Managed two squads (Accounts & CloudSync). Spec-first approach, EventModeling, EventSourcing. Focus on testing (unit, e2e, integration). OSS tool: PrestaShop Flashlight. Stack: GCP, GitHub Actions.

\job{Senior Developer – PrestaShop (Remote)}{Jul 2020 – Jul 2022}{2 yrs}
Scalable backend development. Multi-store data sync. French healthcare platform. Stack: Node.js, NestJS, GCP.

\job{Senior Developer – Fairly (Remote)}{Mar 2025 – present}{ongoing}
Scrum mastering, monitoring, CI/CD. Stack: React, Vite, Docker, PostgreSQL.

\job{Pre-Sales Engineer / Lead Dev – Hoppen}{2016 – 2020}{4 yrs}
Enterprise pre-sales, healthcare system integration, accessibility, home automation, security.

\sectiontitle{Education}
\textbf{Engineering degree (ENIB)} -- 2007–2012\\
International semester: \textit{University of Cadiz, Spain}

\sectiontitle{Languages}
English: fluent \textbullet{} Italian: fluent \textbullet{} Spanish: intermediate \textbullet{} German: beginner

\sectiontitle{Key Skills}
\begin{itemize}
  \item \skill{Management}: coaching, delivery, roadmap planning
  \item \skill{Methodologies}: Agile, TDD, EventSourcing, CI/CD
  \item \skill{Tech}: Node.js, TypeScript, GCP, PostgreSQL
  \item \skill{Ops}: Docker, Linux, Ansible, systemd
\end{itemize}

\sectiontitle{Interests}
Wildlife photography, climbing, species conservation, open-source gastronomy.
\end{document}
